---
title: "Gapminder"
author: "Heathcliff Neels"
date: "11/03/2021"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)


library(tidyverse)

```

## Introduction
In this document,we will be exploring the Gapminder dataset

## observations from the Gapminder dataset
### Countries with life expectancy less than 30
```{r echo=FALSE}
data("gapminder")
gapminder %>% filter (lifeExp <30) %>% select(country)

n <- nrow(gapminder %>% filter (lifeExp <30) %>% select(country))
```

Unfortunately there *have* been countries with low life expectancies. There were `r n` countries that had this situation

### Countries with life expectancy over age 81
```{r, echo=FALSE}

gapminder %>% filter (lifeExp > 81) %>% select(country, year) 
n <- nrow(gapminder %>% filter (lifeExp > 81) )

```
There are `r n` countries where life expectancy has exceeded 81 years

### Life Expectancy by Continent in 2007
```{r, echo=FALSE}
smry1 <- data.frame(filter(gapminder,year == 2007))

boxplot(lifeExp~continent, data=smry1)

```
```{r}
bestcntry <- gapminder$country[which.max(gapminder$lifeExp)]
```
* The country with the higest life expectancy is `r bestcntry`.




